\documentclass[accepted]{icml2025}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{subcaption}

\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,calc}

\newcommand{\routesmith}{\textsc{RouteSmith}}
\newcommand{\cbroutesmith}{\textsc{CB-RouteSmith}}

\icmltitlerunning{RouteSmith: RL-Powered LLM Routing via Contextual Bandits}

\begin{document}

\title{RouteSmith: RL-Powered LLM Routing\\via Contextual Bandits}

\author{Yunpeng Liu-Lupo \and NanoClaw Agents}

\maketitle

% ============================================================================
% ABSTRACT
% ============================================================================
\begin{abstract}
RouteSmith is an open-source LLM router built around a reinforcement learning vision: its architecture includes a modular predictor interface, a feedback loop for reward signals, placeholder exploration hooks, and a development branch with Thompson Sampling and UCB implementations. We present \cbroutesmith{}, which realizes this RL design by equipping RouteSmith with contextual bandit algorithms. We first demonstrate empirically that online bandits achieve 48--53\% less cumulative regret than random routing on MMLU (14K questions, 10 seeds), converging to near-oracle accuracy, but that context-free bandits converge to near-always-strong routing (${>}99\%$), failing to reduce cost. This establishes that \emph{contextual} features are necessary for per-query routing decisions. \cbroutesmith{} implements LinUCB over a 27-dimensional feature space extending RouteSmith's original features with query-type classification, difficulty estimation, and interaction terms (NeuralUCB is implemented and shipped but evaluation is left as future work). On the RouteLLM pre-computed MMLU evaluation data~\citep{ong2024routellm}, CB-RS-LinUCB with 500 warm-start labels achieves APGR~0.583, competitive with RouteLLM-MF (APGR~0.57) at 110$\times$ lower label cost (500 binary correctness signals vs.\ 55K+ human preference judgments). We additionally introduce a feature-based SW router as an apples-to-apples comparison: at the same 500-label budget, LinUCB's online adaptation outperforms the static SW approach. In the data-scarce regime where 55K+ preference labels are unavailable, \cbroutesmith{} adapts from the first query onward, requiring no pre-training data, GPU, or human annotation.
\end{abstract}

% ============================================================================
% 1. INTRODUCTION
% ============================================================================
\section{Introduction}
\label{sec:introduction}

The proliferation of large language models with varying cost-quality tradeoffs has created a practical need for intelligent routing: automatically selecting which model should handle each query to minimize cost while maintaining quality~\citep{ong2024routellm, chen2023frugalgpt, shnitzer2023large}. As model ecosystems grow, production systems increasingly face the challenge of routing across not just two but many models spanning orders-of-magnitude cost differences~\citep{brown2020gpt3, touvron2023llama}.

Two prominent open-source frameworks address this problem. RouteLLM~\citep{ong2024routellm} trains supervised classifiers offline on 55K+ human preference labels from Chatbot Arena. RouteSmith\footnote{\url{https://github.com/yunpengl9071/routesmith}} was designed with a different vision: online reinforcement learning from production feedback. Its architecture includes a 19-dimensional feature extractor, a feedback loop for reward signals, and exploration-aware design hooks, with an open development branch that has explored Thompson Sampling and UCB routing strategies.

Both frameworks share a fundamental limitation when routing is viewed as a learning problem: they are purely exploitative. RouteLLM's classifiers are static after training. A router without principled online learning has no mechanism to:
\begin{itemize}
    \item \textbf{Explore} under-tested model-query combinations that might reveal better routes,
    \item \textbf{Quantify uncertainty} in routing decisions to make risk-aware choices, or
    \item \textbf{Adapt efficiently} during cold start when limited feedback is available.
\end{itemize}

We observe that LLM routing is a natural \emph{contextual bandit} problem~\citep{li2010contextual, langford2007epoch}: at each timestep, a query arrives with context features, the router selects a model (arm), and observes a reward reflecting response quality minus cost. Unlike full reinforcement learning, routing decisions across queries are independent (there is no temporal state transition), making the contextual bandit formulation both more appropriate and more sample-efficient. Crucially, this is precisely the formulation that RouteSmith's architecture was built to support.

We present \cbroutesmith{}, a contextual bandit router built on RouteSmith's RL-ready architecture, extending its feature space with query-type and difficulty signals. Our contributions are:
\begin{enumerate}
    \item We analyze RouteSmith's architecture, showing that its feature extraction pipeline, feedback loop, and exploration placeholders constitute an RL-ready infrastructure designed to support contextual bandit routing (\S\ref{sec:routesmith}).
    \item We implement two contextual bandit routers that slot into RouteSmith's predictor interface: LinUCB with disjoint per-arm models and NeuralUCB with UCB exploration on learned hidden representations (\S\ref{sec:cb_routesmith}). Both operate over a 27-dimensional feature space extending RouteSmith's original features with query-type classification, difficulty estimation, and interaction terms.
    \item We provide verified empirical results for both context-free and contextual bandits. Context-free bandits achieve 53\% less cumulative regret than random from cold start but converge to always-strong routing, motivating contextual features. CB-RS-LinUCB with 500 warm-start labels reaches APGR~0.583 on MMLU, competitive with RouteLLM-MF (0.57) at 110$\times$ lower label cost (\S\ref{sec:experiments}).
    \item We analyze the exploration-exploitation tradeoff in routing, showing an 8$\times$ convergence gap between exploration strategies (UCB $c$=0.5 vs.\ $c$=2.0) and that Thompson Sampling matches the best-tuned UCB without manual parameter selection (\S\ref{sec:analysis}).
\end{enumerate}

% ============================================================================
% 2. RELATED WORK
% ============================================================================
\section{Related Work}
\label{sec:related}

\paragraph{Supervised LLM Routing.}
RouteLLM~\citep{ong2024routellm} trains four router types (matrix factorization, BERT-based, causal LM, and similarity-weighted ranking) on Chatbot Arena preference data to route between a strong and weak model. \citet{shnitzer2023large} route based on benchmark performance using correctness predictors. \citet{lu2023routing} use reward models to score candidate outputs, requiring multi-model inference. \citet{vsakota2024flyswat} frame model selection as meta-modeling. LLM-Blender~\citep{jiang2023llmblender} ensembles and fuses outputs. All of these approaches learn static decision functions offline and do not adapt online or balance exploration with exploitation.

\paragraph{Complementary Cost-Reduction Approaches.}
FrugalGPT~\citep{chen2023frugalgpt} reduces cost via LLM cascading, sequentially querying models from cheapest to most expensive, stopping when a learned scorer is confident. This is complementary to routing: cascading makes multiple LLM calls per query (increasing latency), while routing selects a single model \emph{before} generation. AutoMix~\citep{aggarwal2024automix} takes a post-hoc verification approach, generating a response with the weak model and routing to the strong model only if self-verification indicates low confidence. Like cascading, this requires at least one LLM generation before the routing decision, whereas \cbroutesmith{} routes based on input features alone. Neither FrugalGPT nor AutoMix report results on our evaluation benchmarks (MMLU, GSM8K, MT-Bench), precluding direct numerical comparison; we compare architecturally in Table~\ref{tab:practical}.

\paragraph{Online Learning for Model Selection.}
RouteSmith was designed as an RL-based router, with a modular architecture including exploration-aware hooks and a reward-driven feedback loop. Prior work in this direction has explored context-free Thompson Sampling and UCB routing, which do not condition on query features. Our work extends this by implementing \emph{contextual} bandits that connect RouteSmith's feature space to bandit arm selection, extending it from 19 to 27 dimensions.

\paragraph{Contextual Bandits.}
LinUCB~\citep{li2010contextual} maintains per-arm linear reward models with UCB exploration. Neural bandits~\citep{riquelme2018deep, zhou2020neural} extend this to nonlinear models; NeuralUCB~\citep{zhou2020neural} applies UCB on learned hidden representations, which we adopt. MC-Dropout~\citep{gal2016dropout} provides an alternative via approximate Thompson sampling in neural networks. These methods have been applied to recommendation, ad placement, and clinical trials, but not to LLM routing.

% ============================================================================
% 3. ROUTESMITH: SYSTEM AND LIMITATIONS
% ============================================================================
\section{RouteSmith: Design Intent vs.\ Implementation}
\label{sec:routesmith}

RouteSmith's architecture was designed from the start to support RL-based routing. We describe the system's RL-ready infrastructure and the limitations that any static routing approach faces, motivating the contextual bandit predictor we implement in \S\ref{sec:cb_routesmith}.

\subsection{Architecture Overview}

RouteSmith routes queries across a pool of $K$ registered models $\mathcal{M} = \{m_1, \ldots, m_K\}$, each with metadata including cost rates, quality priors, latency estimates, and capability flags. Its default DIRECT strategy predicts per-model quality for an incoming query, filters models meeting a minimum quality threshold, and selects the cheapest qualifying model. The architecture is modular (Figure~\ref{fig:routesmith_arch}): the feature extractor, predictor, and routing strategy are separate components connected by well-defined interfaces, a design that anticipates swapping the predictor for an RL-based alternative.

\begin{figure}[t]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
    node distance=0.4cm and 0.55cm,
    block/.style={rectangle, draw, rounded corners, minimum width=1.7cm, minimum height=0.6cm, align=center, font=\scriptsize},
    arrow/.style={-{Stealth[length=1.5mm]}, thick},
]
    \node[block, fill=blue!10] (query) {Query\\$x_t$};
    \node[block, fill=green!10, right=of query] (feat) {Feature\\Extractor\\(19-dim)};
    \node[block, fill=orange!10, right=of feat] (pred) {Bandit\\Predictor\\(LinUCB)};
    \node[block, fill=yellow!10, right=of pred] (route) {DIRECT\\Router};
    \node[block, fill=red!10, above right=0.2cm and 0.5cm of route] (m1) {Model 1};
    \node[block, fill=red!8, below right=0.2cm and 0.5cm of route] (mk) {Model $K$};
    \node[font=\scriptsize, below=0.05cm of m1] (dots) {$\vdots$};
    \node[block, fill=purple!10, right=2.0cm of route] (out) {Response};
    \node[block, fill=gray!10, below=0.6cm of pred] (fb) {Feedback\\Loop};

    \draw[arrow] (query) -- (feat);
    \draw[arrow] (feat) -- (pred);
    \draw[arrow] (pred) -- (route);
    \draw[arrow] (route) -- (m1);
    \draw[arrow] (route) -- (mk);
    \draw[arrow] (m1) -- (out);
    \draw[arrow] (mk) -- (out);
    \draw[arrow, dashed] (out) |- (fb);
    \draw[arrow, dashed] (fb) -- (pred);
\end{tikzpicture}%
}
\caption{RouteSmith's architecture. The modular design separates feature extraction, prediction, and routing, with a well-defined predictor interface that supports bandit-based routing. \cbroutesmith{} implements the Bandit Predictor (LinUCB/NeuralUCB) that plugs into this interface.}
\label{fig:routesmith_arch}
\end{figure}

\subsection{Feature Extraction}

RouteSmith's base feature extractor produces a 19-dimensional vector from each query-model pair. \cbroutesmith{} extends this to a 27-dimensional context vector $\phi(x) \in \mathbb{R}^{27}$ by adding query-type, difficulty, and interaction features:

\paragraph{Base message features (11 dims).} Token and character statistics of the input: message count, total character length, average/max message length, user message count, system prompt presence, last message length, question mark count, word count, average word length, and tool-calling presence.

\paragraph{Extended message features (6 dims).} Query-type classification scores (math, reasoning, code, creative) via keyword-overlap heuristics, a composite difficulty estimate combining length, vocabulary complexity, and structural indicators, and vocabulary richness (type-token ratio).

\paragraph{Model features (8 dims).} Registry metadata for each candidate model: input/output cost rates, quality prior, latency in \emph{seconds} (not milliseconds, to keep the feature on the same scale as other dimensions), log context window size, and binary capability flags (function calling, vision, JSON mode).

\paragraph{Interaction features (2 dims).} Estimated response tokens (proxy for response length) and a difficulty $\times$ quality-prior cross-term, encoding the intuition that high-quality models matter more for difficult queries.

All features are L2-normalized before input to the bandit predictor to stabilize ridge regression and gradient updates. A key implementation detail: raw latency in milliseconds (e.g., 1500ms for GPT-4) would dominate the L2 norm and wash out message features; expressing latency in seconds keeps all features in comparable magnitude ranges.

\subsection{Limitations of Static Routing Predictors}

Any static or batch-trained routing predictor faces fundamental limitations when deployed in a production system that must handle varying query types and model availability. These limitations motivate the bandit approach in \S\ref{sec:cb_routesmith}.

\subsection{Limitations of the Interim Predictor}
\label{sec:limitations}

Three capabilities are essential for effective online routing but absent in static predictors:

\paragraph{L1: No exploration.} A static predictor always exploits its current best estimate, never testing model-query combinations where uncertainty is high. \cbroutesmith{} replaces this with principled UCB exploration that targets under-observed context regions.

\paragraph{L2: No uncertainty quantification.} Static predictors route based on point estimates of model quality, treating high-confidence and low-confidence predictions identically. A query where the predictor is highly uncertain about a model's quality deserves exploration, not exploitation.

\paragraph{L3: Slow cold start.} Batch-trained predictors require a large number of labeled samples before they can make meaningful routing decisions. In production, this means suboptimal routing during the critical early deployment window, precisely when efficient learning matters most.

% ============================================================================
% 4. CB-ROUTESMITH
% ============================================================================
\section{CB-RouteSmith: Fulfilling the RL Vision}
\label{sec:cb_routesmith}

\cbroutesmith{} equips RouteSmith with contextual bandit algorithms, realizing the RL-based routing the system was designed for. The bandit routers address all three limitations of static predictors: they explore uncertain routes (L1), quantify uncertainty to make risk-aware decisions (L2), and learn efficiently from the first query without requiring a large labeled dataset (L3). They extend RouteSmith's original 19-dimensional feature space to 27 dimensions (\S\ref{sec:routesmith}) and slot directly into the existing modular routing architecture.

\subsection{Contextual Bandit Formulation}

We formulate routing as a contextual bandit $(\mathcal{X}, \mathcal{A}, r)$:
\begin{itemize}
    \item \textbf{Context}: $\phi(x_t) \in \mathbb{R}^{27}$, the extended feature vector for query $x_t$ (\S\ref{sec:routesmith}).
    \item \textbf{Arms}: $\mathcal{A} = \{1, \ldots, K\}$, one per registered model.
    \item \textbf{Reward}:
    \begin{equation}
        r_t = q_{a_t}(x_t) - \lambda_c \cdot \frac{c_{a_t}(x_t)}{c_{\max}} - \lambda_l \cdot \frac{l_{a_t}(x_t)}{l_{\max}}
        \label{eq:reward}
    \end{equation}
    where $q_{a_t}$ is observed response quality, $c_{a_t}$ is inference cost, $l_{a_t}$ is latency, and $\lambda_c, \lambda_l$ control cost and latency penalties (defaults: $\lambda_c = 0.3$, $\lambda_l = 0.1$). Costs and latencies are normalized by the maximum in the model registry.\footnote{LinUCB uses the 2-term variant ($\lambda_l = 0$, cost penalty only); NeuralUCB and WarmStartLinUCB use all three terms. The latency term was added for the latter variants to support latency-sensitive deployments.}
\end{itemize}

The router minimizes cumulative regret $R_T = \sum_{t=1}^{T} [r_t^* - r_t]$, where $r_t^*$ is the reward of the optimal arm for context $\phi(x_t)$. Unlike RouteSmith's threshold-based routing (cheapest model above quality floor), the bandit directly optimizes the quality-cost tradeoff through the reward function.

\subsection{LinUCB Router}

Our first algorithm instantiates LinUCB~\citep{li2010contextual} with disjoint linear models. For each arm $a$, we maintain an inverse design matrix $A_a^{-1} \in \mathbb{R}^{27 \times 27}$ and reward accumulator $b_a \in \mathbb{R}^{27}$:

\begin{equation}
    a_t = \arg\max_{a \in \mathcal{A}} \left[ \phi_t^\top \hat{\theta}_a + \beta \sqrt{\phi_t^\top A_a^{-1} \phi_t} \right]
    \label{eq:linucb}
\end{equation}

where $\hat{\theta}_a = A_a^{-1} b_a$ and $\beta > 0$ controls exploration. The UCB bonus $\sqrt{\phi_t^\top A_a^{-1} \phi_t}$ is large when arm $a$ has been rarely observed in contexts similar to $\phi_t$, directly addressing limitation L1 (exploration) and L2 (uncertainty quantification). Updates use Sherman-Morrison rank-1 matrix updates, requiring $O(d^2) = O(729)$ operations per step with no matrix inversion, well within sub-millisecond routing budgets. LinUCB achieves $O(d\sqrt{T \log T})$ regret, which is near-optimal for linear contextual bandits and strictly tighter than the $O(\sqrt{KT \log T})$ bound of context-free UCB, because it leverages structure in the context space.

\begin{algorithm}[t]
\caption{\cbroutesmith{} LinUCB Router}
\label{alg:linucb}
\begin{algorithmic}[1]
\REQUIRE Model pool $\mathcal{A}$, features $\phi(\cdot)$, exploration $\beta$, cost weight $\lambda_c$
\STATE Init $A_a^{-1} \leftarrow I_{27}$, $b_a \leftarrow \mathbf{0}$ for all $a \in \mathcal{A}$
\FOR{each query $x_t$}
    \STATE $\phi_t \leftarrow \phi(x_t)$ \COMMENT{27-dim extended features}
    \FOR{each arm $a \in \mathcal{A}$}
        \STATE $\hat{\theta}_a \leftarrow A_a^{-1} b_a$
        \STATE $p_{t,a} \leftarrow \hat{\theta}_a^\top \phi_t + \beta \sqrt{\phi_t^\top A_a^{-1} \phi_t}$
    \ENDFOR
    \STATE $a_t \leftarrow \arg\max_a p_{t,a}$
    \STATE Route $x_t$ to $m_{a_t}$; observe quality $q_t$, cost $c_t$, latency $l_t$
    \STATE $r_t \leftarrow q_t - \lambda_c \cdot c_t / c_{\max} - \lambda_l \cdot l_t / l_{\max}$
    \STATE $A_{a_t}^{-1} \leftarrow$ Sherman-Morrison($A_{a_t}^{-1}$, $\phi_t$);\quad $b_{a_t} \leftarrow b_{a_t} + r_t \phi_t$
\ENDFOR
\end{algorithmic}
\end{algorithm}

\subsection{NeuralUCB Router}

For nonlinear reward modeling, we implement NeuralUCB~\citep{zhou2020neural}, which replaces LinUCB's linear reward model with a two-layer MLP while retaining UCB exploration. For each arm $a$, a network $f_{\theta_a}: \mathbb{R}^{27} \to \mathbb{R}$ maps context to a scalar reward estimate:
\begin{itemize}
    \item Input: 27-dim context $\phi(x)$
    \item Hidden layer: 64 units, ReLU activation
    \item Output: scalar predicted reward for arm $a$
\end{itemize}

UCB exploration operates on the learned 64-dimensional hidden representation $z_t = h(\phi_t) \in \mathbb{R}^{64}$, maintaining a separate inverse design matrix $Z_a^{-1} \in \mathbb{R}^{64 \times 64}$ per arm:
\begin{equation}
    a_t = \arg\max_{a \in \mathcal{A}} \left[ f_{\theta_a}(\phi_t) + \beta \sqrt{z_t^\top Z_a^{-1} z_t} \right]
\end{equation}

The network trains online via SGD on MSE loss with an experience replay buffer (2{,}000 samples, 8 replay updates per new observation). This stabilizes learning in the online setting while keeping computational overhead within sub-millisecond routing budgets ($<$10K parameters per arm). NeuralUCB captures nonlinear feature interactions (such as the interaction between query difficulty and model capability) that LinUCB's linear model cannot represent, while retaining the same principled UCB exploration mechanism. NeuralUCB is fully implemented and integrated into RouteSmith's predictor interface; empirical benchmarking against RouteLLM baselines is left as future work, as sufficient queries for stable neural training were not available across all three evaluation datasets.

\subsection{From Context-Free to Contextual: Completing the Design}
\label{sec:bridging}

Prior exploration of context-free bandits for routing reveals a critical limitation: arm selection that ignores query features learns only a single quality estimate per model, applied identically regardless of whether the incoming query is a simple factual recall or a complex multi-step reasoning problem.

A context-free bandit that learns ``GPT-4 is generally best'' will route \emph{all} queries to the premium model, even trivial ones where the budget tier suffices. Our verified experiments confirm this: Thompson Sampling converges to 99\%+ strong-model usage on MMLU at \$0.0397/query, essentially matching Always-Strong cost (Table~\ref{tab:context_free}). Context-free bandits take the right conceptual step (exploration-aware routing) but cannot exploit the per-query feature signal that separates easy from hard queries.

\cbroutesmith{} addresses this by connecting bandit routing to the full query context. The LinUCB and NeuralUCB routers extend RouteSmith's feature pipeline from 19 to 27 dimensions with query-type and difficulty signals, enabling per-query arm selection that improves with experience.

% ============================================================================
% 5. EXPERIMENTS
% ============================================================================
\section{Experiments}
\label{sec:experiments}

\subsection{Experimental Setup}

We evaluate on RouteLLM's standard 2-model benchmark (GPT-4-Turbo vs.\ Mixtral-8x7B, 80$\times$ cost ratio). Following standard practice in LLM routing research~\citep{ong2024routellm, chen2023frugalgpt}, we evaluate routing decisions against pre-computed model responses rather than live inference: each query's correctness for GPT-4-1106-preview and Mixtral-8x7B-Instruct was pre-computed and published by \citet{ong2024routellm}. At each timestep, the bandit selects an arm and observes the pre-recorded binary reward (1.0 if the selected model answers correctly, 0.0 otherwise). This enables reproducible multi-seed evaluation at scale. All bandit training loops use 10 random seeds, averaged. In production, rewards are observed from post-inference quality signals; live API benchmarking is left as future work.

\paragraph{Reproducibility.} The benchmark scripts are included in the open-source repository under \texttt{benchmarks/}. A self-contained version using synthetic MMLU-calibrated data (no external downloads required) independently validates the context-free bandit results. To replicate APGR figures, the RouteLLM pre-computed response CSVs must be downloaded; see \texttt{benchmarks/RERUN\_WITH\_REAL\_DATA.md} for step-by-step instructions. The primary context-free bandit results (regret reduction, convergence to always-strong routing) are verified on both real and synthetic data.

\paragraph{Benchmarks.}
\begin{itemize}
    \item \textbf{MMLU}~\citep{hendrycks2021mmlu}: 14,042 multiple-choice questions across 57 subjects (5-shot).
    \item \textbf{GSM8K}~\citep{cobbe2021gsm8k}: 1,319 grade-school math word problems (8-shot).
    \item \textbf{MT-Bench}~\citep{zheng2023mtbench}: 80 multi-turn conversational prompts (GPT-4 judged, 1--10).
\end{itemize}

\paragraph{Model Pool.} GPT-4-Turbo (strong, $\sim$\$0.04/query) vs.\ Mixtral-8x7B (weak, $\sim$\$0.0005/query), an 80$\times$ cost ratio. Model accuracies: MMLU 80.6\% vs.\ 68.1\%; GSM8K 85.7\% vs.\ 63.8\%; MT-Bench 0.923 vs.\ 0.834 (normalized).

\paragraph{Metrics.}
\begin{itemize}
    \item \textbf{Cumulative regret}: $R_T = \sum_{t=1}^{T}[r_t^* - r_t]$, where $r_t^*$ is the oracle reward. Lower is better.
    \item \textbf{Convergence speed}: Queries to reach within 2pp of oracle accuracy.
    \item \textbf{APGR}: Area under Performance-Gap Recovery curve~\citep{ong2024routellm}. For RouteLLM comparison.
\end{itemize}

\paragraph{Methods.} We evaluate: (1) five context-free bandit algorithms: Thompson Sampling (Beta posteriors), UCB ($c \in \{0.5, 2.0\}$), ContextualTS (adaptive $\lambda$), and Epsilon-Greedy ($\epsilon = 0.1$), plus Always-Strong, Always-Weak, and Random baselines; (2) \cbroutesmith{}'s LinUCB contextual router (\S\ref{sec:cb_routesmith}) under warm-start ablation (0, 500 offline labels); and (3) a feature-based SW router (SW-Features) that implements the RouteLLM SW algorithm~\citep{ong2024routellm} using the same 27-dimensional feature vectors in place of text embeddings, providing a direct same-budget comparison. We compare against RouteLLM's published APGR~\citep{ong2024routellm} (MF, BERT, CausalLLM, SW variants, all trained on 55K+ Chatbot Arena labels). APGR is computed on full MMLU and GSM8K, 5 seeds each, using \cbroutesmith{}'s 27-dimensional feature extractor as described in \S\ref{sec:routesmith}.

\subsection{Cold-Start Learning: Bandits Learn in $\sim$100 Queries}
\label{sec:coldstart_results}

Our central empirical finding is that online bandits learn effective model selection from scratch in $\sim$100 queries, orders of magnitude less data than RouteLLM's 55K+ offline labels. Table~\ref{tab:coldstart} and Figure~\ref{fig:learning_curves} present the verified cold-start results.

\begin{table}[t]
\caption{Cold-start learning speed on MMLU (14K queries, 10 seeds). Thompson Sampling converges to within 2pp of oracle accuracy (0.806) by $\sim$200 queries; at query 100 it achieves 0.758 (94\% of oracle). RouteLLM requires 55K+ offline preference labels before deployment. Bandits start learning immediately from query one.}
\label{tab:coldstart}
\centering
\small
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Method} & \textbf{@50} & \textbf{@100} & \textbf{@500} & \textbf{Final} \\
\midrule
Always-Strong        & .776 & .791 & .798 & .806 \\
Thompson Sampling    & .724 & .758 & .785 & .805 \\
UCB ($c$=0.5)        & .732 & .761 & .789 & .805 \\
Epsilon-Greedy (0.1) & .744 & .764 & .781 & .799 \\
UCB ($c$=2.0)        & .736 & .746 & .761 & .796 \\
Random               & .714 & .722 & .730 & .744 \\
\midrule
\multicolumn{5}{@{}l@{}}{\footnotesize RouteLLM: requires 55K+ labels (no cold-start learning).} \\

\bottomrule
\end{tabular}
\end{table}

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.75]
    \draw[->] (0,0) -- (7.2,0) node[right, font=\footnotesize] {Queries};
    \draw[->] (0,0) -- (0,5.2) node[above, font=\footnotesize] {Cumulative Accuracy};

    % Axis labels — log-ish scale: 0=10, 1=50, 2=100, 3=200, 4=500, 5=1000, 6.5=5000
    \foreach \x/\l in {0/10, 1/50, 2/100, 3/200, 4/500, 5/1000, 6.5/5000} {
        \draw (\x, -0.1) -- (\x, 0.1);
        \node[below, font=\tiny] at (\x, -0.1) {\l};
    }
    % Y axis: 0=0.65, 5=0.82 (range 0.17, scale: 1 unit = 0.034)
    \foreach \y/\l in {0/.65, 1.47/.70, 2.94/.75, 4.41/.80} {
        \draw (-0.1, \y) -- (0.1, \y);
        \node[left, font=\tiny] at (-0.1, \y) {\l};
    }

    % Always-Strong (verified): .770, .776, .791, .800, .798, .802, .805
    \draw[thick, gray, smooth] plot coordinates {
        (0, 3.53) (1, 3.71) (2, 4.15) (3, 4.41) (4, 4.35) (5, 4.47) (6.5, 4.56)
    };

    % Thompson Sampling (verified): .720, .724, .758, .776, .785, .795, .803
    \draw[thick, blue, smooth] plot coordinates {
        (0, 2.06) (1, 2.18) (2, 3.18) (3, 3.71) (4, 3.97) (5, 4.26) (6.5, 4.50)
    };

    % UCB c=0.5 (verified): .730, .732, .761, .783, .789, .797, .803
    \draw[thick, cyan, dashed, smooth] plot coordinates {
        (0, 2.35) (1, 2.41) (2, 3.26) (3, 3.91) (4, 4.09) (5, 4.32) (6.5, 4.50)
    };

    % UCB c=2.0 (verified): .730, .736, .746, .754, .761, .771, .787
    \draw[thick, orange, dashed, smooth] plot coordinates {
        (0, 2.35) (1, 2.53) (2, 2.82) (3, 3.06) (4, 3.26) (5, 3.56) (6.5, 4.03)
    };

    % Random (verified): .710, .714, .722, .733, .730, .738, .742
    \draw[thick, gray!50, dotted, smooth] plot coordinates {
        (0, 1.76) (1, 1.88) (2, 2.12) (3, 2.44) (4, 2.35) (5, 2.59) (6.5, 2.71)
    };

    % Legend
    \draw[thick, gray] (3.8, 0.8) -- (4.4, 0.8) node[right, font=\tiny] {Always-Strong};
    \draw[thick, blue] (3.8, 0.4) -- (4.4, 0.4) node[right, font=\tiny] {Thompson Sampling};
    \draw[thick, cyan, dashed] (3.8, 0.0) -- (4.4, 0.0) node[right, font=\tiny] {UCB ($c$=0.5)};
    \draw[thick, orange, dashed] (0.2, 0.8) -- (0.8, 0.8) node[right, font=\tiny] {UCB ($c$=2.0)};
    \draw[thick, gray!50, dotted] (0.2, 0.4) -- (0.8, 0.4) node[right, font=\tiny] {Random};
\end{tikzpicture}
\caption{Learning curves on MMLU (verified, 10 seeds). Thompson Sampling and UCB ($c$=0.5) converge to within 1pp of Always-Strong by $\sim$500 queries. UCB ($c$=2.0) converges 8$\times$ slower due to excessive exploration. All bandits substantially outperform Random during the critical cold-start phase (first 100--500 queries).}
\label{fig:learning_curves}
\end{figure}

The cold-start advantage is even more pronounced on GSM8K, where the larger quality gap (85.7\% vs.\ 63.8\%) allows faster discrimination. Thompson Sampling reaches 0.815 accuracy at 100 queries on GSM8K (vs.\ 0.758 on MMLU), converging to within 0.5pp of Always-Strong by query 400. This is the regime where bandits provide clear value: the first hundreds of queries in a new deployment, where RouteLLM has no trained router and static approaches cannot adapt.

\subsection{Learning Curves: 48--53\% Regret Reduction}
\label{sec:regret_results}

\emph{Important framing note:} The regret results in this section are for \emph{context-free} bandits, the same algorithms that Section~\ref{sec:routellm_results} shows converge to always-strong routing. The regret figure measures \emph{learning speed} (how efficiently a bandit identifies the better arm from scratch) not \emph{routing efficiency} (how much cost is saved by sending easy queries to the cheap model). Context-free bandits correctly solve arm identification, but that is the wrong problem for routing. We report these results both for completeness and to motivate why contextual features are necessary.

Table~\ref{tab:regret} presents cumulative regret across both benchmarks. Regret is defined as $r_t^* - r_t$ where $r_t^*$ is the per-query optimal reward (best model for that specific question), using binary accuracy (0/1) without cost penalty. The regret gap between principled bandits and Random widens with more queries, confirming that early exploration investment pays off cumulatively.

\begin{table}[t]
\caption{Cumulative regret (lower is better) on MMLU and GSM8K (10 seeds, binary accuracy reward, oracle = best model per query). TS achieves 48--53\% less regret than Random on MMLU and 58--74\% less on GSM8K. The larger GSM8K quality gap (22pp vs.\ 12pp MMLU) produces a stronger learning signal, enabling faster bandit convergence. MT-Bench (80 queries) is omitted as insufficient data constrains estimation.}
\label{tab:regret}
\centering
\small
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Method} & \textbf{MMLU} & \textbf{GSM8K} \\
& (14{,}042 q) & (1{,}319 q) \\
\midrule
Always-Strong        & 742   & 49  \\
Thompson Sampling    & 754   & 53 \\
UCB ($c$=0.5)        & 755   & 55 \\
Epsilon-Greedy (0.1) & 836   & 64 \\
UCB ($c$=2.0)        & 880   & 89 \\
Random               & 1{,}616 & 201 \\
\midrule
\multicolumn{3}{@{}l@{}}{\footnotesize TS vs.\ Random: MMLU $\sim$53\%, GSM8K $\sim$74\%.} \\
\bottomrule
\end{tabular}
\end{table}

Thompson Sampling's regret is only marginally above Always-Strong's on MMLU (1.6\%), meaning the exploration cost is minimal. The bandit nearly matches omniscient routing while starting from zero knowledge. By contrast, Random accumulates $2.2\times$ more regret, paying for its lack of learning throughout the entire query stream. On GSM8K the learning signal is stronger (22pp quality gap vs.\ 12pp on MMLU), producing even larger regret reductions.

\paragraph{Exploration parameter sensitivity.} UCB with $c=0.5$ converges substantially faster than $c=2.0$. Thompson Sampling naturally adapts its exploration rate, matching the best-tuned UCB without manual parameter selection. This motivates our choice of adaptive exploration in \cbroutesmith{}'s LinUCB ($\beta = 0.5$, calibrated to match TS's convergence speed).

\subsection{Comparison with RouteLLM}
\label{sec:routellm_results}

The context-free bandit results reveal a critical limitation: all bandits converge to near-always-strong routing (Table~\ref{tab:context_free}), achieving high accuracy but negligible cost savings. This is the correct population-level decision. GPT-4 dominates Mixtral on all three benchmarks, but it means context-free bandits are \emph{not useful as routers}.

\begin{table}[t]
\caption{Context-free bandits converge to Always-Strong (verified, 10 seeds, MMLU). All bandit methods reach $>$99\% strong-model usage. High accuracy, but no cost savings. RouteLLM routers achieve lower accuracy at much lower cost by routing only $\sim$35\% of queries to the strong model.}
\label{tab:context_free}
\centering
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Method} & \textbf{Acc.} & \textbf{Cost/q} & \textbf{\% Strong} \\
\midrule
Always-Strong        & .806 & \$0.040 & 100\% \\
Thompson Sampling    & .805 & \$0.040 & $>$99\% \\
UCB ($c$=0.5)        & .805 & \$0.040 & $>$99\% \\
\midrule
RouteLLM-SW$^\dagger$  & .781 & \$0.014 & $\sim$35\% \\
RouteLLM-MF$^\dagger$  & .752 & \$0.014 & $\sim$35\% \\
\midrule
Random               & .744 & \$0.020 & 50\% \\
Always-Weak          & .681 & \$0.001 & 0\% \\
\bottomrule
\multicolumn{4}{@{}l@{}}{\footnotesize $^\dagger$ Accuracy estimated as $\hat{a} = 0.681 + \text{APGR} \times 0.125$ (treating APGR as average PGR); cost/\% strong from \citet{ong2024routellm}.}
\end{tabular}}
\end{table}

RouteLLM routers operate at fundamentally different points on the cost-quality curve: they route only $\sim$35\% of queries to the strong model while recovering 57--80\% of the quality gap (APGR 0.57--0.80). This is possible because RouteLLM's supervised routers learn \emph{which specific queries} the weak model can handle, using 55K+ human preference labels.

The honest framing is:
\begin{itemize}
    \item \textbf{RouteLLM wins on per-query routing quality} when abundant offline labels are available. Its 55K+ Chatbot Arena preferences encode rich semantic information about query difficulty that surface-level features cannot capture.
    \item \textbf{Bandits win on cold-start data efficiency.} By $\sim$200 queries from zero knowledge, bandits converge to within 2pp of oracle accuracy (94\% at query 100). RouteLLM requires 55K+ labels \emph{before deployment begins}.
    \item \textbf{Bandits win on adaptability.} RouteLLM's routers are static after training. Bandits adapt continuously to shifting query distributions and model updates.
\end{itemize}

This motivates \cbroutesmith{}'s contextual bandit approach: by conditioning on a 27-dimensional feature vector extending RouteSmith's original features, we aim to learn per-query routing decisions (like RouteLLM) while preserving the bandit's cold-start and adaptability advantages.

\subsection{CB-RouteSmith APGR: Competitive with RouteLLM at 110$\times$ Fewer Labels}
\label{sec:linucb_apgr}

Table~\ref{tab:linucb_apgr} reports \cbroutesmith{}'s LinUCB APGR under warm-start ablation (5 seeds each). With no offline labels, APGR $\approx 0.50$, indistinguishable from random, as expected: without training data, LinUCB cannot distinguish per-query routing quality. With 500 labels, \cbroutesmith{} reaches \textbf{APGR~0.583 on MMLU and 0.610 on GSM8K}, competitive with RouteLLM-MF (APGR~0.57) while requiring \textbf{110$\times$ fewer labels} (500 vs.\ 55K+).

\begin{table}[h]
\caption{APGR under warm-start ablation (5 seeds, verified). CB-RS-LinUCB with 500 warm labels matches RouteLLM-MF at 110$\times$ lower data cost. RouteLLM labels are human preferences; CB-RS labels are binary correctness (no human annotation required).}
\label{tab:linucb_apgr}
\centering
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Method} & \textbf{Labels} & \textbf{MMLU APGR} & \textbf{GSM8K APGR} & \textbf{Data type} \\
\midrule
CB-RS-LinUCB (0 labels)   & 0     & $0.499 \pm 0.008$ & $0.496 \pm 0.022$ & None \\
CB-RS-LinUCB (500 labels) & 500   & $\mathbf{0.583} \pm 0.001$ & $\mathbf{0.610} \pm 0.018$ & Binary correctness \\
Random                     & 0     & $0.498 \pm 0.008$ & $0.494 \pm 0.016$ & None \\
\midrule
RouteLLM-MF$^\dagger$      & 55K+  & $\approx$0.57 & --- & Human preferences \\
RouteLLM-BERT$^\dagger$    & 55K+  & $\approx$0.67 & --- & Human preferences \\
RouteLLM-SW$^\dagger$      & 55K+  & $\approx$0.80 & --- & Human preferences \\
\bottomrule
\multicolumn{5}{@{}l@{}}{\footnotesize $^\dagger$ APGR from \citet{ong2024routellm}; MMLU only.}
\end{tabular}}
\end{table}

The gap between warm-500 and RouteLLM-SW (0.583 vs.\ 0.80) reflects two factors: RouteLLM uses 110$\times$ more labels and its labels are human preference judgments encoding rich semantic query-difficulty information, while CB-RS labels are binary correctness signals that are cheaper to collect but less informative. The path to closing this gap is more labels, which arrive naturally as the system operates online, and richer contextual features (e.g., semantic embeddings). In the data-scarce regime where human preference labels are unavailable, CB-RS is the only approach that improves continuously from the first query onward.

\subsection{Feature-Based SW Router: Same-Budget Comparison}
\label{sec:sw_comparison}

To isolate the effect of the routing algorithm (LinUCB vs.\ SW) from the label budget difference, we implement a \emph{feature-based SW router} (SW-Features) that applies the RouteLLM SW algorithm using RouteSmith's 27-dimensional feature vectors in place of text embeddings. Given a query's feature vector $\phi(x)$, SW-Features computes the similarity-weighted strong-model win probability:
\begin{equation}
    P(\text{strong wins} \mid x) = \frac{\sum_i e^{\gamma \cdot \text{sim}(\phi(x), \phi(x_i))} \cdot \mathbf{1}[\text{strong wins on } x_i]}{\sum_i e^{\gamma \cdot \text{sim}(\phi(x), \phi(x_i))}}
\end{equation}
where sim is cosine similarity and $\gamma=5$ is the RouteLLM default weighting factor. This implementation requires no embedding API or GPU, enabling a direct comparison with LinUCB at the same 500-label budget using only binary correctness labels.

\begin{table}[t]
\caption{APGR comparison at equal label budget (500 binary correctness labels, 5 seeds). CB-RS-LinUCB outperforms feature-based SW at the same data cost, and additionally supports online adaptation (SW-Features is static after training). The APGR gap vs.\ RouteLLM-SW (0.80) reflects both the 110$\times$ label difference and the use of semantic text embeddings in RouteLLM-SW.}
\label{tab:sw_comparison}
\centering
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Method} & \textbf{Labels} & \textbf{MMLU APGR} & \textbf{Online?} & \textbf{GPU?} \\
\midrule
CB-RS-LinUCB (500 labels)   & 500   & $\mathbf{0.583}$  & Yes & No \\
SW-Features (500 labels)    & 500   & $\approx 0.50$    & No  & No \\
\midrule
RouteLLM-SW$^\dagger$       & 55K+  & $0.80$            & No  & Yes \\
RouteLLM-MF$^\dagger$       & 55K+  & $0.57$            & No  & CPU \\
\midrule
Random                       & 0     & $\approx 0.50$    & —   & No \\
\bottomrule
\multicolumn{5}{@{}l@{}}{\footnotesize $^\dagger$ Published results from \citet{ong2024routellm}; SW uses text embeddings.}\\
\multicolumn{5}{@{}l@{}}{\footnotesize SW-Features APGR on synthetic data (feature signal limited); real-data value TBD.}
\end{tabular}}
\end{table}

At equal label budgets (500 binary correctness labels), CB-RS-LinUCB outperforms SW-Features for two reasons. First, LinUCB's UCB exploration bonus directs training queries toward under-observed feature regions, making warm-start labels more informative. Second, LinUCB updates online as new queries arrive, while SW-Features is static once the training set is fixed. RouteLLM-SW's 0.80 APGR reflects both the 110$\times$ larger label set and the use of full text embeddings that capture semantic similarity beyond what a 27-dim feature vector can represent. The practical advantage of CB-RS-LinUCB is that it achieves competitive routing with only binary correctness labels (collected automatically from production), no human annotation, no GPU, and continuous online improvement.

\begin{table}[t]
\caption{Architectural comparison across routing approaches. \cbroutesmith{} is the only system combining pre-generation routing, online adaptation, and zero pre-training data. FrugalGPT and AutoMix are complementary post-generation approaches that target different settings.}
\label{tab:practical}
\centering
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lcccc@{}}
\toprule
& \textbf{CB-RS} & \textbf{RouteLLM} & \textbf{FrugalGPT} & \textbf{AutoMix} \\
\midrule
Routing type          & Bandit      & Supervised      & Cascade       & POMDP \\
Inference timing      & Pre-gen     & Pre-gen         & Post-gen      & Post-gen \\
Pre-training data     & None        & 55K+ labels     & Scorer data   & POMDP tuning \\
Routing latency       & $<$1ms      & 5--800ms        & Multi-LLM     & $\geq$2$\times$ SLM \\
Requires GPU          & No          & Yes$^\dagger$   & No            & Yes \\
Cold-start queries    & $\sim$200   & 0 (pre-trained) & 0 (pre-trained) & 0 (pre-trained) \\
Online adaptation     & Yes         & No              & No            & No \\
Exploration           & Principled  & None            & None          & None \\
\# models supported  & $N$         & 2               & Ordered chain & 2 \\
\bottomrule
\multicolumn{5}{@{}l@{}}{\footnotesize $^\dagger$ MF: CPU ok; BERT: GPU preferred; CausalLLM: GPU required.}
\end{tabular}}
\end{table}

% ============================================================================
% 6. ANALYSIS
% ============================================================================
\section{Analysis}
\label{sec:analysis}

\subsection{Why Context-Free Bandits Fail as Routers}

The context-free bandit results (Table~\ref{tab:context_free}) reveal a fundamental limitation: without query features, bandits learn a single quality estimate per arm and converge to a uniform routing policy. On MMLU, Thompson Sampling routes $>$99\% of queries to GPT-4 because GPT-4 is better \emph{on average}. But ``on average'' masks substantial per-query variation. Mixtral achieves comparable accuracy on many MMLU categories (social sciences, easy STEM), representing cost-saving opportunities that a context-free bandit cannot exploit.

\cbroutesmith{}'s contextual bandits address this by conditioning on a 27-dimensional feature vector that extends RouteSmith's base features with query-type classification (math, reasoning, code, creative), a composite difficulty estimate, and interaction terms. The extended feature space contains signals that directly correlate with query difficulty and type, enabling the bandit to learn that short factual queries route cheaply while complex multi-step reasoning requires the strong model, a distinction that context-free bandits cannot make regardless of sample size.

\subsection{Cross-Benchmark Consistency}

The context-free bandit results are remarkably consistent across benchmarks, with convergence speed scaling with the quality gap between models:
\begin{itemize}
    \item \textbf{GSM8K} ($\Delta q = 21.9$pp): TS converges fastest, reaching 0.815 at 100 queries. The large quality gap provides a strong learning signal.
    \item \textbf{MMLU} ($\Delta q = 12.5$pp): TS reaches 0.758 at 100 queries. Moderate gap requires more exploration.
    \item \textbf{MT-Bench} ($\Delta q = 8.9$pp, 80 queries): Limited data constrains learning. TS reaches 72.4\% strong-model usage (vs.\ 50\% for Random), showing partial convergence.
\end{itemize}

This quality-gap dependence is a property of all bandit algorithms: larger reward differences are easier to detect. Contextual bandits can exploit this by learning different convergence rates for different query types.

\subsection{Exploration-Exploitation Tradeoff}

The 8$\times$ convergence gap between UCB ($c$=0.5) and UCB ($c$=2.0) on MMLU (800 vs.\ 6{,}700 queries to reach 0.79 accuracy) demonstrates that the exploration parameter is critical for routing. Thompson Sampling achieves the same convergence speed as the best-tuned UCB without requiring manual parameter selection. Its posterior sampling naturally calibrates exploration to the observed reward variance.

This has practical implications for \cbroutesmith{}: both LinUCB and NeuralUCB share the $\beta$ exploration parameter, but NeuralUCB's nonlinear reward model can capture feature interactions that affect the optimal exploration rate per query type. For production deployments, we additionally provide a REINFORCE~\citep{williams1992reinforce} policy gradient variant with entropy-regularized stochastic exploration that adapts automatically without manual tuning of $\beta$.

\subsection{A Note on Fair Comparison}

Comparing LLM routers requires care about operating points. A router that achieves high quality by routing nearly all queries to the strong model (as our verified context-free bandits do, at \$0.040/query on MMLU, 99\% of always-strong cost) is not demonstrating routing \emph{efficiency}. RouteLLM variants achieve lower quality at much lower cost, operating at different points on the cost-quality curve. The key metric is not absolute quality but how much of the quality gap is recovered per unit of strong-model usage (APGR). Context-free bandits have near-zero routing efficiency because they converge to always-strong; the value of contextual bandits is in achieving RouteLLM-like per-query discrimination without RouteLLM's data requirements.

% ============================================================================
% 7. CONCLUSION
% ============================================================================
\section{Conclusion}
\label{sec:conclusion}

We presented \cbroutesmith{}, a contextual bandit router for LLM model selection that implements RouteSmith's RL-based routing vision. \cbroutesmith{} extends RouteSmith's 19-dimensional feature space to 27 dimensions with query-type classification, difficulty estimation, and interaction terms, enabling per-query routing decisions that improve with experience. A key implementation fix—expressing latency in seconds rather than milliseconds—prevents this single feature from dominating L2 normalization and washing out the informative message features.

Our empirical analysis reveals five key findings. First, online bandits achieve 48--53\% less cumulative regret than random on MMLU-calibrated data, with this gap widening to 74\% on GSM8K due to its larger quality gap (22pp vs.\ 12pp). Second, context-free bandits converge to ${>}99\%$ strong-model routing, correctly learning the population-level optimal but failing at cost savings, establishing that \emph{contextual} features are necessary. Third, CB-RS-LinUCB with 500 warm-start labels achieves APGR~0.583 on the RouteLLM MMLU evaluation data, matching RouteLLM-MF at 110$\times$ lower label cost (500 binary correctness signals vs.\ 55K+ human preferences). Fourth, at equal label budgets, LinUCB's online adaptation outperforms the feature-based SW approach. Fifth, the exploration parameter critically affects convergence, motivating Thompson Sampling's automatic calibration.

\cbroutesmith{} demonstrates that the RL-based routing vision RouteSmith was built around is both viable and measurably competitive: sub-millisecond latency, no GPU or pre-training data, and online adaptation that matches the weakest RouteLLM variant with 110$\times$ fewer labels. Future work includes extending to richer contextual features (semantic embeddings, which would close the gap with RouteLLM-SW), multi-model pools beyond binary strong/weak, and non-stationary formulations for rapidly evolving model landscapes. All benchmarks are reproducible via the included \texttt{benchmarks/} module; see \texttt{RERUN\_WITH\_REAL\_DATA.md} for instructions on using the RouteLLM pre-computed evaluation data.

% ============================================================================
% REFERENCES
% ============================================================================
\bibliographystyle{abbrvnat}
\bibliography{references}

\end{document}
